\documentclass[margin,line]{resume}
\usepackage[colorlinks=true, pdfstartview=FitV, linkcolor=magenta, urlcolor=magenta]{hyperref}
\usepackage{hyperref}
%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Caitlin Baker}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact Information}

   \begin{tabular}{ l c l}
   E-mail: caitbaker@gmail.com &  Address: Dublin City Centre, Ireland\\
   Phone: +353 834777864\\
   GitHub: github.com/caitbaker\\
    \end{tabular}

    %__________________________________________________________________________________________________________________
    % Language skills
    \section{\mysidestyle Language Skills}
    Fluent in English, Portuguese and Spanish.
       
    %__________________________________________________________________________________________________________________
    % Computer skills
    \section{\mysidestyle Computer \\Skills}
    Microsoft Office, LaTex, SAP, Oracle and Salesforce.com. 
    
    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}
    \textbf{Dalarna University}, Borlange, Sweden \vspace{2mm}\\\vspace{1mm}%
    \textsl{Master of Arts (MA), Tourism Destination Development}\hfill \textbf{ 2013 -- 2014}\\
    \textbf{Escola Superior de Tecnologia e Gestao}, IPVC, Viana do Castelo, Portugal \vspace{2mm}\\\vspace{1mm}%
    \textsl{BA in Tourism}\hfill \textbf{ 2004 -- 2008}\\

    %__________________________________________________________________________________________________________________
    % Professional Experience

    \section{\mysidestyle Professional\\Experience}  
    \textbf{Bulgari Ireland}, Dublin, Ireland \vspace{2mm}\\\vspace{1mm}%
    \textsl{Customer Service Representative} \hfill \textbf{March 2015 -- Present}\\*
    \begin{itemize}
    \item Manage customer orders (entering in system, availability and price). 
    \item Interaction with the Credit team to release orders. 
    \item Respond to customer queries and resolve any issues that may come up. 
    \item Continuous communication with other departments. 
    \end{itemize}       
      
    \textbf{FanFootage}, Dublin, Ireland \vspace{2mm}\\\vspace{1mm}%
    \textsl{Event Coordinator Internship} \hfill \textbf{September 2014 -- February 2015}\\*
    \begin{itemize}
    \item Organising sales pipeline by centralising and standardising artist reach-outs. 
    \item Produce shows within FanFootage as they happen. This involves communicating with various stakeholders. 
    \item Approving videos for use in various events. 
    \item Reaching out to various artists to understand their needs/restrictions at events. 
    \end{itemize}     
    
    \textbf{Nexeo Solutions Central Office Europe}, Barcelona, Spain \vspace{2mm}\\\vspace{1mm}%
    \textsl{Customer Service Representative} \hfill \textbf{June 2012 -- June 2013}\\*
    \begin{itemize}
    \item Back office management and support for Portuguese sales team.
    \item Inputting orders into SAP, attention to detail when introducing quantity and pricing.
    \item Printing invoices and confirming delivery dates. 
    \item Management of customers' e-mails, faxes and phone calls.
    \item Business development 
    \item Back-up for Spanish and Reception/Office Administration
    \end{itemize}
    
    \textbf{Hotusa Hotels S.A.}, Barcelona, Spain \vspace{2mm}\\\vspace{1mm}%
    \textsl{Hotel Reservations Agent} \hfill \textbf{December 2011 -- February 2012}\\*
    \begin{itemize}
    \item Reserving accommodation for clients and agencies via telephone and e-mail. 
    \item Answering inquiries pertaining to hotel services, B2B and B2C. 
    \end{itemize}
    \clearpage
    
    \textbf{Luxottica Iberia S.A.}, Barcelona, Spain \vspace{2mm}\\\vspace{1mm}%
    \textsl{Call Centre Agent} \hfill \textbf{July 2011 -- November 2011}\\*
    \begin{itemize}
    \item Customer service B2B through phone, e-mail and fax. 
    \item Inputting orders and resolving problems. 
    \end{itemize}
    
    \textbf{Groundforce}, Barcelona, Spain \vspace{2mm}\\\vspace{1mm}%
    \textsl{Check-in Agent} \hfill \textbf{January 2011 -- May 2011}\\*
    \begin{itemize}
    \item Passenger and baggage check-in. 
    \item Passenger boarding. 
    \item Customer service. 
    \end{itemize}
    
    \textbf{Cirque Du Soleil}, Barcelona, Spain \vspace{2mm}\\\vspace{1mm}%
    \textsl{Usher} \hfill \textbf{November 2010 -- January 2011}\\*
    \begin{itemize}
    \item Greeting attendees and seating them. 
    \item Answering queries in regards to the show. 
    \item Problem solving. 
    \end{itemize}

    \textbf{Ryanair LTD}, Stansted Airport, United Kingdom \vspace{2mm}\\\vspace{1mm}%
    \textsl{Cabin Crew} \hfill \textbf{September 2009 -- March 2010}\\*
    \begin{itemize}
    \item Passenger service. 
    \item Operational and security processes. 
    \item Problem solving. 
    \item On board sales. 
    \end{itemize}
    
 
   	% Hobbies
    \section{\mysidestyle Hobbies}
    Reading, travelling, hiking, researching, spending time with friends, listening to music and dancing.

    %___________________
    % Refs
    \section{\mysidestyle References} 
    Available on request.
    


\end{resume}
\end{document}
%______________________________________________________________________________________________________________________
% EOF
